### 2020-08-04 docs/msc_thesis_figures.Rmd
bettre figs update 2

---
title: "Msc Thesis Figures"
author: "Valentin Lucet"
date: "17/07/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'index.html')) })
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '5'
---

@@

No outputs for github page

@@

  mxp <- 1e1000 # 10000

@@

  ggsave(plot = final_plot, filename = paste0("../thesis/figures/",names[class]), width = the_width, height = the_height, dpi = the_dpi)
}
```

@@

bar_chap2 <- all_chap2 %>% 
  mutate(value = ifelse(.$value>10, 10, .$value)) %>%
  mutate(new_class = ifelse(.$value == 10, "forest", .$new_class)) %>% 
  group_by(new_class, timestep, scenario, value) %>% 
  summarise(area = sum(area)) %>% ungroup() %>% 
  filter(value %in% c(1,2,10)) %>% 
  left_join(results_clean, by = c("scenario"="scenarioId")) %>% 
  mutate(value = as.factor(value), timestep = as.factor(timestep)) %>% 
  ggplot(aes(fill=timestep, y=area, x=new_class)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values = bi_colors) +
  facet_wrap(~name, labeller = label_wrap_gen(width = 30)) +
  theme(legend.position = c(0.85, 0.7)) +
  labs(x = "Land use Class", 
       y = "Mean Area (hectare)", 
       fill = "Year") +
  NULL
bar_chap2
ggsave("../thesis/figures/bar_chap2.png", bar_chap2, 
       width = the_width, height = 20, dpi = the_dpi)
```

>>>>

---
title: "Msc Thesis Figures"
author: "Valentin Lucet"
date: "17/07/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'index.html')) })
output:
  html_document:
    df_print: paged
    code_folding: hide
    self_contained: yes
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '5'
---

@@

@@

  mxp <- 1e10000 # 1000

@@

  ggsave(plot = final_plot, filename = paste0("../thesis/figures/",names[class]), width = 20, height = 10, dpi = the_dpi)
}
```

### Land use maps

```{r message=TRUE, warning=TRUE}
source('~/Documents/Master/Thesis/land_con_monteregie/scripts/functions/draw_scenario.R')
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp)
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot, 
         filename = paste0("../thesis/figures/",the_name), width = 20, height = 10, dpi = the_dpi)
}

```

@@

bar_chap2 <- all_chap2 %>% 
  mutate(value = ifelse(.$value>10, 10, .$value)) %>%
  mutate(new_class = ifelse(.$value == 10, "forest", .$new_class)) %>% 
  group_by(new_class, timestep, scenario, value) %>% 
  summarise(area = sum(area)) %>% ungroup() %>% 
  filter(value %in% c(1,2,10)) %>% 
  left_join(results_clean, by = c("scenario"="scenarioId")) %>% 
  mutate(value = as.factor(value), timestep = as.factor(timestep)) %>% 
  ggplot(aes(fill=timestep, y=area, x=new_class)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values = bi_colors) +
  facet_wrap(~name, labeller = label_wrap_gen(width = 30)) +
  theme(legend.position = c(0.9, 0.8)) +
  labs(x = "Land use Class", 
       y = "Mean Area (hectare)", 
       fill = "Year") +
  NULL
bar_chap2
ggsave("../thesis/figures/bar_chap2.png", bar_chap2, 
       width = the_width, height = 20, dpi = the_dpi)
```

### 2020-08-04 thesis/appendix_1.tex
bettre figs update 2

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/BAU_compare.png}
}
 \caption{Comparison of Monteregie at the beginning of the BAU simulation in 2010, and at the end in 2100 (BAU-Baseline scenario).}
 \label{fig:BAU_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/Ref_compare.png}
}
 \caption{Comparison of Monteregie at the beginning of the Reforestation simulation in 2010, and at the end in 2100 (BAU-Reforestion-Baseline scenario).}
 \label{fig:Ref_compare}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/Corr_compare.png}
}
 \caption{Corr).}
 \label{fig:Corr_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/CorrRef_compare.png}
}
 \caption{CorrRef).}
 \label{fig:	CorrRef_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/CorrRefTar_compare.png}
}
 \caption{CorrRefTar.}
 \label{fig:	CorrRefT_compare}
\end{figure}

>>>>

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/scenario_39_compare.png}
}
 \caption{Comparison of Monteregie at the beginning of the BAU simulation in 2010, and at the end in 2100 (BAU-Baseline scenario).}
 \label{fig:BAU_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/scenario_42_compare.png}
}
 \caption{Comparison of Monteregie at the beginning of the Reforestation simulation in 2010, and at the end in 2100 (BAU-Reforestion-Baseline scenario).}
 \label{fig:Ref_compare}
\end{figure}

@@

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/scenario_45_compare.png}
}
 \caption{Corr).}
 \label{fig:Corr_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/scenario_48_compare.png}
}
 \caption{CorrRef).}
 \label{fig:	CorrRef_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=\textwidth]{thesis/figures/scenario_51_compare.png}
}
 \caption{CorrRefTar.}
 \label{fig:	CorrRefT_compare}
\end{figure}
